Incentivizing Exploration with Unbiased History

### 2018-11-02 intro.tex
Added a sentence on focus groups.
Some edits in intro/3Level

The first step is to obtain any substantial improvement over the full-disclosure policy. We accomplish this with a relatively simple policy which runs the full-disclosure policy ``in parallel" on several disjoint subsets of agents,  collects all data from these runs and discloses it to all remaining agents. While any single run of the full-disclosure policy may get stuck on a suboptimal arm, having these parallel runs ensure that sufficiently many of them will ``get lucky" and provide some exploration. This simple policy achieves $\tilde{O}(T^{2/3})$ regret. Conceptually, it implements a basic bandit algorithm that explores uniformly for a pre-set number of rounds, then picks one arm for exploitation and stays with it for the remaining rounds. We think of this policy  as having two ``levels": Level 1 contains the parallel runs, and Level 2 is everything else.

The next step is to implement \emph{adaptive exploration}, where the exploration schedule is adapted to previous observations. This is needed to improve over the $\tilde{O}(T^{2/3})$ regret. We upgrade the simple two-level policy with a middle level, where agents receive the data collected in some (but not all) runs from the first level. Essentially, this new level provides exploration only if the gap $\Delta$ between the best and second-best arm is small, but not small enough to be insignificant to the regret guarantee.  When this happens, the runs in the first level do not have sufficient time to distinguish the two arms before herding on one of them.  However, for each of these arms, there is some chance that it has an empirical mean reward significantly above its actual mean while the other one has empirical mean reward significantly below its actual mean in any given first-level run.  The second level agents observing such runs will be induced to further explore that arm, allowing the third level agents to get enough samples to distinguish the arms.
%
The main result extends this construction to multiple levels, connected in fairly intricate ways, obtaining optimal regreat of $\tilde{O}(T^{1/2})$. \ascomment{add more}. \nicomment{don't think it's necessary; at least i can't crystalize the key idea it adds over the 3level; mostly it just takes the 3level idea to its extreme}

\ascomment{stable-ish text up to here.}

>>>>

The first step is to obtain any substantial improvement over the full-disclosure policy. We accomplish this with a relatively simple policy which runs the full-disclosure policy ``in parallel" on several disjoint subsets of agents,  collects all data from these runs and discloses it to all remaining agents. In practice, these subsets may correspond to multiple ``focus groups". While any single run of the full-disclosure policy may get stuck on a suboptimal arm, having these parallel runs ensure that sufficiently many of them will ``get lucky" and provide some exploration. This simple policy achieves $\tilde{O}(T^{2/3})$ regret. Conceptually, it implements a basic bandit algorithm that explores uniformly for a pre-set number of rounds, then picks one arm for exploitation and stays with it for the remaining rounds. We think of this policy  as having two ``levels": Level 1 contains the parallel runs, and Level 2 is everything else.

The next step is to implement \emph{adaptive exploration}, where the exploration schedule is adapted to previous observations. This is needed to improve over the $\tilde{O}(T^{2/3})$ regret. As a proof of concept, we focus on the case of two actions, and upgrade the simple two-level policy with a middle level. The agents in this new level receive the data collected in some (but not all) runs from the first level. What happens is that these agents explore only if the gap $\Delta$ between the best and second-best arm is sufficiently small, and exploit otherwise. When $\Delta$ is small, the runs in the first level do not have sufficient time to distinguish the two arms before herding on one of them.  However, for each of these arms, there is some chance that it has an empirical mean reward significantly above its actual mean while the other arm has empirical mean reward significantly below its actual mean in any given first-level run.  The middle-level agents observing such runs will be induced to further explore that arm, collecting enough samples for the third-level agents to distinguish the two arms. The main result extends this construction to multiple levels, connected in fairly intricate ways, obtaining optimal regreat of $\tilde{O}(T^{1/2})$.
